Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-07-13 ltx/data_paper/DataPaper.tex
added plots for kernel support experiment

>>>>

\begin{figure}
\subfloat[][]{\includegraphics[scale=.8]{./Figures/KernelSupportForObservationNoise0.pdf}}
\subfloat[][]{\includegraphics[scale=.8]{./Figures/KernelSupportForObservationNoise01.pdf}}
\subfloat[][]{\includegraphics[scale=.8]{./Figures/KernelSupportForObservationNoise018.pdf}}
\caption{{\bf Kernel support approximation for different values of synaptic time constant, $\tau$ and observation noise variance, $\sigma^2_{\varepsilon}$}. Each subplot shows normalised connectivity kernel estimate. (\textbf a) $\sigma_{\varepsilon}^2$=0. (\textbf b) $\sigma_{\varepsilon}^2$=0.1 . (\textbf c) $\sigma_{\varepsilon}^2$=0.18.}
\label{fig:KernelWidthEstimationExperiment}
The effect of the observation noise variance on the connectivity kernel support is very much like to that of disturbance covariance function where an initial guess can be made in a similar manner. To study how synaptic parameter, $\xi=1-\frac{ T_s}{\tau}$, influence the resultant support of the connectivity kernel different values of synaptic time constatnt, $\tau$, were considered in a physiologically plausible range while noting that its value should be also higher than the sampling time. In fact synaptic parameter in \eqref{eq:EM-Fourier_TF_of_Kernel}  acts like a scaling factor, dilating or shrinking the estimated support, as the subtracting a constant in a frequency domain only affects the value at the origin in the spatial domain. The result of the correlation analysis for the connectivity kernel is shown in Figure~\ref{fig:KernelWidthEstimationExperiment} where each subplot is the normalised  estimate for varying synaptic time constants while the observation noise was kept constant. Note that for clarification the amplitude at the origin was negated when the chosen values of $\tau$ and $\sigma^2_{\varepsilon}$ resulted in the negative values at the origin.
